Collective excitations in competing phases in two and three dimensions

### 2024-03-07 paper/main.tex
Poster

Furthermore, we have found a peak in $\spectral{CDW}$ that appears at large values of $V$, 
which is most likely the same as the one found close to the CDW-AFM phase transition. 
\textcolor{red}{It is also reasonable to assume, that this peak is always located outside of the two-particle continuum, even for small values of $V$.
In this case however, it would lie very close to the continuum, which we cannot resolve due to the limited accuracy of our numerics.
Therefore, it appears as a singularity at $2\Delta$.}

@@

\textcolor{red}{Specifically for the SC related quantities, one can fathom including a coupling of the electronic system to the electromagnetic field.}
This should move the position of the phase mode close to the plasma frequency as explained by the Anderson-Higgs mechanism.

@@

%==============================================================================
% Acknowledgments 
%==============================================================================
\begin{acknowledgments} 
    ....
\end{acknowledgments}

@@

Lastly, all remaining peaks below the two-particle continuum behave identical.
The real part of each one of them behaves as $1/\omega$ in close vicinity to the peak position.
This indicates that the peaks are $\delta$ distributions.
The peaks of $\spectral{l.AFM}$ and $\spectral{CDW}$ close the the phase transition are identical when swapped, 
i.e., $\spectral{l.AFM}$ in the CDW phase is the same as $\spectral{CDW}$ in the AFM phase.

>>>>

Furthermore, we have found a peak in $\spectral{CDW}$ that appears at large values of $V$, 
which is most likely the same as the one found close to the CDW-AFM phase transition. 
\textcolor{red}{It is also reasonable to assume, that this peak is always located outside of the two-particle continuum, even for small values of $V$.
In this case, however, it would lie very close to the continuum, which we cannot resolve due to the limited accuracy of our numerics.
Therefore, it appears as a singularity at $2\Delta$.}

@@

\textcolor{red}{Specifically for the SC-related quantities, one can fathom including a coupling of the electronic system to the electromagnetic field.}
This should move the position of the phase mode close to the plasma frequency as explained by the Anderson-Higgs mechanism.

@@

%==============================================================================
% Acknowledgments 
%==============================================================================
\begin{acknowledgments} 
    \textcolor{red}{This research was partially funded by the MERCUR Kooperation.
    We would like to thank the members of our group for various useful discussions.
    [Oder hier lieber alle mal beim Namen nennen? Ich hab mich ja mit allen mal unterhalten]
    [Götz Seibold zu danken klingt meines Erachtens auch sinnig, mit dem hast du ja viel gesprochen.
    Lido habe ich nicht verwendet.]}
\end{acknowledgments}

@@

Lastly, all remaining peaks below the two-particle continuum behave identically.
The real part of each one of them behaves as $1/\omega$ in close vicinity to the peak position.
This indicates that the peaks are $\delta$ distributions.
The peaks of $\spectral{l.AFM}$ and $\spectral{CDW}$ close the phase transition are identical when swapped, 
i.e., $\spectral{l.AFM}$ in the CDW phase is the same as $\spectral{CDW}$ in the AFM phase.
